Manuscript

### 2014-09-16 inst/simulation/manuscript.Rmd
...

```{r figure-4b}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1])

@@

```{r figure-5}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
a <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5.png", width=4, height=2)
```

>>>>

```{r figure-4b}
study <- getStudy(scenario="A")
validation <- Validation(study=study, populationSizeOverEstimate=20000)
populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1])

@@

```{r figure-5a}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
a <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5a.png", width=4, height=2)
```

```{r figure-5b}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames, probs=c(.25, .75), probsName="50%")
credibilityIntervals <- rbind(a, b)

p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Interval, colour=modelName)) + geom_point() +
  scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
  theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
  xlab("Scenario") + ylab("Proportion within CI")
print(p)
saveFigure(p, "manuscript-figure-5b.png", width=4, height=2)
```
